Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-10-01 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
plot more gravityWave results and further analyse them

The initial thermal profile is subtracted from the potential temperature field at the end of the integration to reveal the structure of thermal anomalies.
Results are similar across all grid types and resolutions, but examining the anomalies in the lee of the mountain errors are found in the lowest few layers: the bottommost layer is anomalously warm and the layer above it is anomalously cold.  \TODO{this isn't true at all resolutions, e.g. 50dz is cold at the bottom}  At all resolutions, the amplitude of the errors is greater on the cut cell grid than the BTF \TODO{or SLEVE?} grid.  As resolution increases, the anomalously cold layers first increase in amplitude, then begin to span multiple layers, which suggests that the errors are controlled by the mountain height. \TODO{that conclusion might be stronger with tests at different mountain heights?  oh no, not more tests! :-P}

To summarize, results of the gravity waves test on all grids are in good agreement with the reference solution from \citet{melvin2010}.

@@

>>>>

The initial thermal profile is subtracted from the potential temperature field at the end of the integration to reveal the structure of thermal anomalies.
Results are similar across all grid types and resolutions but, examining the anomalies in the lee of the mountain, errors are found in the lowest few layers.  Errors are generated on the lee slopes of the mountain and are advected to the outlet boundary, forming striped anomalies.  At resolution of $\Delta z > \SI{50}{\meter}$, the lowest layer is anomalously warm and the layer above is anomalously cold.  As resolution increases, the anomalously cold layer first increases in amplitude, then the cold anomaly begins to span multiple layers.  At $\Delta z = \SI{50}{\meter}$, the structure is reversed, having lower layers that are too cold and layers above that are too warm.  At all resolutions, the amplitude and height of the errors are greater on the cut cell grid compared to the BTF \TODO{or SLEVE?} grid.

To summarize, results of the gravity waves test on all grids are in good agreement with the reference solution from \citet{melvin2010}.  Stripes of potential temperature anomalies are found in the lee of the mountain, and these errors are most severe on the cut cell grid.  \TODO{say we want to find out what's causing them}

@@

\begin{figure*}
	\centering
	\includegraphics[width=6in]{../fig-gravityWaves/fig-gravityWaves.pdf}
%
	\caption{\TODO{}}
	\label{fig:gw}
\end{figure*}
